A Comparison of Graph Processing Systems

### 2020-09-21 documentation/paper/main.tex
discussion
most introductions done
hugepages section

\section{Evaluation}
\todo{Einleitung}

@@

@@

>>>>

\section{Evaluation}
The main part of this paper is the evaluation, which consists of two parts. The first is a description and explanation of our testing environment and methodology. Followed by a lengthy presentation and discussion of the test results of the frameworks.

@@

\bibitem{virtual_memory}
\BIBentryALTinterwordspacing
E.~Abrossimov, M.~Rozier, and M.~Shapiro, ``Generic virtual memory management
  for operating system kernels,'' in \emph{Proceedings of the Twelfth ACM
  Symposium on Operating Systems Principles}, ser. SOSP '89.\hskip 1em plus
  0.5em minus 0.4em\relax New York, NY, USA: Association for Computing
  Machinery, 1989, p. 123–136. [Online]. Available:
  \url{https://doi.org/10.1145/74850.74863}
\BIBentrySTDinterwordspacing

@@

\bibitem{superpages}
M.~Gorman and P.~Healy, ``Performance characteristics of explicit superpage
  support,'' in \emph{Computer Architecture}, A.~L. Varbanescu, A.~Molnos, and
  R.~van Nieuwpoort, Eds.\hskip 1em plus 0.5em minus 0.4em\relax Berlin,
  Heidelberg: Springer Berlin Heidelberg, 2012, pp. 293--310.

### 2020-09-21 documentation/paper/sections/preliminiaries.tex
hugepages section

\subsection{Hugepages}
\todo{Section schreiben}
\cite{hugepages}

>>>>

\subsection{Hugepages}
Most systems in use today use a so-called virtual memory management \cite{virtual_memory}.
It is implemented in the kernel and represents an abstraction between the memory devices of a machine and the individual programs.
Each program gets its own virtual leading address space.
This simplifies the implementation of applications considerably and also increases security, since each program can only access its own virtual address space.
The address areas are organized in so called pages, which in most cases are 4 KiB in size.
In the Translation lookaside buffer (TBL) the most recent translations of virtual memory to physical memory are cached.

Translating from the virtual to the physical address space significantly reduces the performance of today's data processing systems, since the size of the RAM grows much faster than the size of the TBL \cite{hugepages, superpages}.
To counteract this problem, hugepages were developed, which are usually several mibibibytes in size.
This minimizes the CPU time needed for table lookups, because there are much less TBL misses.
This speedup is especially noticeable in applications that are very memory intensive, like graph processing systems.
